---
title: "HW: Joining and Manipulating Data"
subtitle: "STT2860 Intro to Data Mgmt and Visualization" 
author: "PUT YOUR NAME HERE"
date: "`r format(Sys.time(), '%A, %B %d, %Y @ %I:%M %p')`"
output: 
  html_document: 
    theme: cosmo
    highlight: textmate
    toc: true
    toc_depth: 4
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

Names of people you worked with: 

***

### Packages

```{r}
library(tidyverse)
library(nycflights13)
library(skimr)
```

You will use the `nycflights13` datasets discussed in [Section 3.7 of Modern Dive](https://moderndive.com/3-wrangling.html#joins) to complete the problems below.

### Problem 1: Mutating Joins & Data Manipulation

#### Flights from Newark

Filter the `flights` dataset for only those flights originating at Newark Liberty International Airport (EWR). Store this dataset as `flights_ewr`. Remove the `origin` variable, since it is no longer needed. Use `glimpse()` to visualize the structure.

Check: You should have 120,835 observations and 18 variables in `flights_ewr`.

```{r}
flights_ewr <- filter(flights, origin == "EWR")
flights_ewr <- select(flights_ewr, -origin)
glimpse(flights_ewr)
```

#### Find Top 5 Destinations

Use `count()`, `arrange()`, and `slice_head()` to find and display the five most common destination airports for planes departing from Newark.

```{r}
top_destinations <- flights_ewr %>%
  count(dest, sort = TRUE) %>%
  arrange(desc(n)) %>%
  slice_head(n = 5)
```

#### Flights to Top 5 Destinations

Filter your `flights_ewr` dataset so that it contains only flights to the top five destinations. Save this new dataset as `flights_ewr_top5`. Use `glimpse()` to visualize the structure.

Check: You should have 26,602 observations and 18 variables in `flights_ewr_top5`.

```{r}
flights_ewr_top5 <- flights_ewr %>%
  filter(dest %in% top_destinations$dest)
glimpse(flights_ewr_top5)
```

#### Add Destination Names

Choose only the FAA airport code and airport name from the `airports` dataset and then join the result to the `flights_ewr_top5` datset so that we get a dataset that now contains the names of the destination airports (but *only* those names---no names that are not part of the top five).  We want to keep all of the flights. Change the variable name `faa` to `dest_code` and airport `name` to `dest_name`. Do all of these manipulations in a single piped sequence and save the new dataset as the object `flights_ewr_top5_dest`. Use `glimpse()` to visualize the structure.

Check: You should have 26,602 observations and 19 variables in `flights_ewr_top5_dest`.

```{r}
flights_ewr_top5_dest <- flights_ewr_top5 %>% 
  left_join(select(airports, faa, name), by = c("dest" = "faa")) %>% 
  rename(dest_name = 'name', dest_code = 'faa')
glimpse(flights_ewr_top5_dest)
```

#### Add Carrier Codes

Join the `flights_ewr_top5_dest` and `airlines` datasets so that we get a dataset that includes carrier names for the airlines that fly out of Newark to the top five destinations (but *only* those carrier names). Again, we want to keep all the flights, even if the carrier name is not in the `airlines` dataset. Change the new variable `name` to `carrier_name` and `flight` to `flight_num`. Move the carrier code, carrier name, and flight number variables to a position right after the destination name variable. Do all of these manipulations in a single piped sequence and save the new dataset as the object `flights_ewr_top5_dest_carrier`. Use `skim()` to visualize the structure.

Check: You should have 26,602 observations and 20 variables in `flights_ewr_top5_dest_carrier`.

```{r}
flights_ewr_top5_dest_carrier <- flights_ewr_top5_dest %>%
  left_join(select(airlines, carrier, name), by = "carrier") %>%
  select(dest_name, dest_code, carrier, carrier_name, flight_num, tailnum, year, month, day, dep_time, sched_dep_time, dep_delay, arr_time, sched_arr_time, arr_delay) %>%
  skim()

```

### Problem 2: Filtering Joins & Data Manipulation

#### Flights That Have Plane Information

Use one of the filtering joins to determine how many cases in `flights_ewr_top5_dest_carrier` have plane information in the `planes` dataset. Save the dataset as `planes_yes` and use `nrow()` to display the number of cases.  

```{r}
planes_yes <- flights_ewr_top5_dest_carrier %>%
  filter(!is.na(tailnum))
nrow(planes_yes)
```

#### Flights That Do Not Have Plane Info

Use one of the filtering joins to determine how many cases in `flights_ewr_top5_dest_carrier` do not have plane information in the `planes` dataset. Save the dataset as `planes_yes` and use `nrow()` to display the number of cases. 

Hint: The number of observations in `planes_yes` and `planes_no` should add up to 26,602.

```{r}
planes_no <- flights_ewr_top5_dest_carrier %>%
  filter(is.na(tailnum))
nrow(planes_no)
```

#### Pull the Tail Numbers (With Info)

Use `distinct()`, `arrange()`, and `pull()` to create a vector `tailnum_yes` that contains all of the the unique tail numbers in the `planes_yes` dataset in alphanumeric order. Use `length()` to show how many values are in the vector.

```{r}
tailnum_yes <- planes_yes %>%
  distinct(tailnum) %>%
  arrange(tailnum) %>%
  pull(tailnum)
length(tailnum_yes) # number of values in the vector
```

#### Pull the Tail Numbers (No Info)

Use `distinct()`, `arrange()`, and `pull()` to create a vector `tailnum_no` that contains all of the the unique tail numbers in the `planes_no` dataset in alphanumeric order. Use `length()` to show how many values are in the vector. Since it is relatively short, also print out the vector to visualize it.

```{r}
tailnum_no <- planes_no %>%
  distinct(tailnum) %>%
  arrange(tailnum) %>%
  pull(tailnum)
length(tailnum_no) # number of values in the vector
print(tailnum_no) # print the vector
```

***
```{r}
sessionInfo()
```