---
title: "Annual Inflation Dataset<br>Consumer Price Index (CPI) Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`annualinflation.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/annualinflation.csv)<br>
<i class="fas fa-database"></i> [`cpidata19132023.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cpidata19132023.csv)

### Description

Annual US inflation from December to December (i.e., December YOY), calculated using Consumer Price Index (CPI) for all urban consumers. For example, the Dec-Dec inflation for 2021 is as follows. You can multiply by 100 to express as a percentage.

$$\frac{CPI_{\text{Dec 2021}} - CPI_{\text{Dec 2020}}}{CPI_{\text{Dec 2020}}}%$$

### Variables---Annual Inflation Dataset

* `year`: calendar year
* `decade`: decade, year 19X0 to 19X9 and 20X0 to 20X9
* `inflationYOY`: December YOY inflation rate (e.g., 0.126 = 12.6%)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/annualinflation.csv")
glimpse(DATA)
head(DATA)
tail(DATA)
```

### Variables---Consumer Price Index Dataset

* `year`: calendar year
* `Jan`: January CPI values
* `Feb`: February CPI values
* `Mar`: March CPI values
* `Apr`: April CPI values
* `May`: May CPI values
* `Jun`: June CPI values
* `Jul`: July CPI values
* `Aug`: August CPI values
* `Sep`: September CPI values
* `Oct`: October CPI values
* `Nov`: November CPI values
* `Dec`: December CPI values

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cpidata19132023.csv")
glimpse(DATA)
head(DATA)
tail(DATA)
```

### References

[US Inflation Calculator: Consumer Price Index Data from 1913 to Present](https://www.usinflationcalculator.com/inflation/consumer-price-index-and-annual-percent-changes-from-1913-to-2008/)
