---
title: "Atlantic Hurricanes 1851-2020 Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      echo = FALSE,
                      comment = NA)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`ATLhurricanes18512020.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/ATLhurricanes18512020.csv)

### Description

Data about Atlantic Ocean hurricanes from 1851 to 2020. The Atlantic hurricane season is roughly from June through November. Tropical cyclones in the North Atlantic are called hurricanes, tropical storms, or tropical depressions.

### Variables

* Year: calendar year
* Named: number of named storms
* Hurricanes: number of hurricanes
* Major: number of major hurricanes (Category 3 and higher)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/ATLhurricanes18512020.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: StatCrunch public datasets 

Landsea, Chris and Blake, Eric. (June 30, 2021). ["Was 2020 a Record-Breaking Hurricane Season? Yes, But..."](https://noaanhc.wordpress.com/2021/06/30/was-2020-a-record-breaking-hurricane-season-yes-but/) Inside the Eye, the Offical Blog of the National Hurricane Center.

<hr>

