---
title: "Bloomberg Billionaires Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`billionaires_2021_10_31.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Kaggle/billionaires_2021_10_31.csv)

<i class="fas fa-database"></i> [`billionaires_2021_10_31_raw.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Kaggle/billionaires_2021_10_31_raw.csv)



### Description

The [Bloomberg Billionaires Index](https://www.bloomberg.com/billionaires/) is a daily ranking of the world’s 500 richest people. More details are given on each billionaire’s profile page (may require a subscription). Monetary values and list rankings are updated at the close of every stock trading day in New York City. This dataset is from October 31, 2021.

### Variables

* `Rank`: person's rank on the list
* `Name`: person's name
* `Total_Net_Worth`: raw value of net worth as given on Bloomberg
* `Total_Net_Worth_Bil`: numeric net worth in billions of dollars
* `LastChange`: raw value for change in net worth as given on Bloomberg
* `LastChange_Bil`: numeric change in net worth in billions of dollars
* `YTDChange`: raw value for year-to-date change in net worth as given on Bloomberg
* `YTDChange_Bil`: numeric year-to-date change in net worth in billions of dollars
* `Country`: person's country of citizenship
* `Industry`: person's primary industry

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Kaggle/billionaires_2021_10_31.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: [Billionaire's Index | Kaggle](https://www.kaggle.com/datasets/kkhandekar/billionaires-index)

<hr>
