---
title: "Body Temperatures Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      echo = FALSE,
                      comment = NA)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`bodytemps.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/bodytemps.csv)

### Description

These data are derived from a dataset used in Mackowiak, P. A., Wasserman, S. S., and Levine, M. M.  (1992), "A Critical Appraisal of 98.6 Degrees F, the Upper Limit of the Normal Body Temperature, and Other Legacies of Carl Reinhold August Wunderlich," *Journal of the American Medical Association*, 268(12), 1578-1580. They were constructed to match as closely as possible the histograms and summary statistics presented in that article by Shoemaker, A. L., (1996). "What's Normal? -- Temperature, Gender, and Heart Rate," *Journal of Statistics Education*, 4(2).

Some questions we could investigate with these data include:

1. Is the distribution of body temperatures normal?
2. Is the true population mean really 98.6 degrees F?
3. At what temperature should we consider someone's temperature to be "abnormal"?
4. Is there a significant difference in normal temperature between males and females?
5. Is there a relationship between people's normal body temperatures and heart rates?
6. Does it matter that the original temperatures were measured on the Celsius scale?

### Variables

* sex: whether the person was male or female (as a binary, since this is older data)
* tempF: the person's body temperature in degrees Fahrenheit
* heartbpm: the person's pulse in beats perminute 

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/bodytemps.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: http://jse.amstat.org/v4n2/datasets.shoemaker.html 

