---
title: "Capital Punishment Dataset<br>Size of Death Row Dataset<br>Executions Since 1976 Dataset<br>Death Row Demographics Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`cappunish20231018.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cappunish20231018.csv)

<i class="fas fa-database"></i> [`deathrowsize.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/deathrowsize.csv)

<i class="fas fa-database"></i> [`executions19762022.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/executions1976to2022.csv)

<i class="fas fa-database"></i> [`deathrowrace.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/deathrowrace.csv)

### Description

Data about the death penalty in the United States as of October 18, 2023.

### Variables---Capital Punishment Dataset

* `state`: state name (including District of Columbia)
* `region`: US Census region
* `division`: US Census regional subdivision
* `court`: US Court of Appeals regional circuit 
* `dp1`: whether or not the state legally has the death penalty (yes/no)
* `dp2`: `dp1` but also indicates states that have a governor's moratorium
* `abolished`: year capital punishment was legally abolished in the state
* `post1976`: number of executions after 1976 (state only)
* `pre1976`: number of executions before 1976 (may include federal/military)
* `prisoners`: total number of prisoners currently on death row
* `women`: number of women on death row (subset of `prisoners`)
* `freed`: number of innocent people later freed from death row
* `clemency`: number of people who were granted clemency
* `felony`: whether someone can get the death penalty as a felony accessory
* `sentence`: who decides on whether someone gets a death penalty sentence

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cappunish20221106.csv")
glimpse(DATA)
head(DATA)
```

### Variables---Size of Death Row Dataset

Number of prisoners on death row for each year from 1968 to 2022.

* `year`: year
* `total`: total prisoners on death row

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/deathrowsize.csv")
glimpse(DATA)
head(DATA)
```

### Variables---Executions Since 1976 Dataset

Number of executions per year for each state, DC, and the federal government.

* `state`: state (including District of Columbia and Federal Government)
* `yxxxx`: year (number of executions for each year from 1976 to 2022)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/executions1976to2022.csv")
glimpse(DATA)
head(DATA)
```

### Variables---Death Row Demographics Dataset

State-by-state death row populations by race as of January 1, 2022.

* `state`: state name (including US Government and US Military)
* `black`: number of black death row inmates
* `white`: number of white death row inmates (non-latinx)
* `latinx`: number of latinx death row inmates
* `nativeam`: number of native american death row inmates
* `asian`: number of asian death row inmates
* `unknown`: number of death row inmates with unknown race/ethnicity

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/deathrowrace.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: [Death Penalty Information Center](https://deathpenaltyinfo.org)

* [State by State](https://deathpenaltyinfo.org/state-and-federal-info/state-by-state)
* [Size of Death Row by Year](https://deathpenaltyinfo.org/death-row/overview/size-of-death-row-by-year)
* [Racial Demographics](https://deathpenaltyinfo.org/death-row/overview/demographics)

[Census Regions and Divisions of the United States](https://www2.census.gov/geo/pdfs/maps-data/maps/reference/us_regdiv.pdf)

[United States Court of Appeals Circuit Map](https://www.uscourts.gov/sites/default/files/u.s._federal_courts_circuit_map_1.pdf)

[Legal Information Institute: Furman v. Georgia (1972)](https://www.law.cornell.edu/wex/furman_v_georgia_(1972))

<hr>
