---
title: "Cereals Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`cereals.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cereals.csv)

### Description

Students collected nutrition label information from cereals in a Wegman's supermarket (circa early 1990s). The nutrition variables in the dataset are for one serving. Missing data is indicated by `-1`.

### Variables

* name: cereal name
* mfr: manufacturer
   * A = American Home Food Products
   * G = General Mills
   * K = Kellogg's
   * N = Nabisco
   * P = Post
   * Q = Quaker Oats
   * R = Ralston Purina
* type
   * C (cold)
   * H (hot)
* calories: calories
* protein: grams of protein
* fat: grams of fat
* sodium: milligrams of sodium
* fiber: grams of dietary fiber
* carbo: grams of complex carbohydrates
* sugars: grams of sugars
* potass: milligrams of potassium
* vitamins: vitamins and minerals
   * 0 = none added
   * 25 = enriched, often to 25% FDA recommended
   * 100 = 100% of FDA recommended
* shelf: display shelf (1, 2, or 3, counting from floor)
* weight: weight in ounces
* cups: number of cups
* rating: Consumer Reports rating

```{r glimpsedata}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cereals.csv")
glimpse(DATA)
```

### References

* https://www.kaggle.com/crawford/80-cereals 
* https://www.kaggle.com/crawford/80-cereals/discussion/154053

<hr>
