---
title: "Cereals Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<hr>

<i class="fas fa-database"></i> [cereals.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cereals.csv)


### Description

Students collected nutrition information from the nutrition labels of cereals in one supermarket.


### Variables

* name: cereal name
* mfr: manufacturer
* calories: number of calories
* sugars: grams of sugar
* carbo: grams of carbohydrates
* protein: grams of protein
* fat: grams of fat
* sodium: milligrams of sodium
* fiber: grams of fiber
* potass: milligrams of potassium
* shelf: shelf on which the cereal was displayed
* Middle: middle shelf?
* shelf_1: shelf 1 or not
* shelf_2: shelf 2 or not
* shelf_3: shelf 3 or not

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cereals.csv")
glimpse(DATA)
```


### References

Source: https://dasl.datadescription.com/datafile/cereals/

