---
title: "Rollercoasters Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`coasters2015.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/coasters2015.csv)

### Description

The [Roller Coaster Database](https://rcdb.com/) gathers information about every roller coaster in the world, past or present. This dataset contains data for coasters that were new in 2015.

### Variables

* Name: coaster name
* Park: park where the rollercoaster is located
* Track: steel or wooden coaster
* Speed: speed in mph
* Height: maximum height in feet
* Drop: maximum drop in feet
* Length: length in feet
* Duration: ride time in seconds
* Inversions: do the riders turn upside down at any point?

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/coasters2015.csv")
glimpse(DATA)
```

### References

Source: https://dasl.datadescription.com/datafile/coasters-2015/

[Roller Coaster Database Census Report](https://rcdb.com/census.htm)

<hr>
