---
title: "Couples Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<hr>

<i class="fas fa-database"></i> [couples.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/couples.csv)


### Description

This dataset contains a sample of married couples.


### Variables

* Names: names of the husband and wife
* wAge: wife's age in years
* hAge: husband's age in years
* wHeight: wife's height in millimeters
* hHeight: husband's height in millimeters

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/couples.csv")
glimpse(DATA)
```


### References

Source: https://dasl.datadescription.com/datafile/couples/

Chalabi, M. (2014, December 4). How Common Is It For A Man To Be Shorter Than His Partner? [Blog post]. Retrieved from https://fivethirtyeight.com/features/how-common-is-it-for-a-man-to-be-shorter-than-his-partner/

Stulp G, Buunk AP, Pollet TV, Nettle D, Verhulst S (2013) Are Human Mating Preferences with Respect to Height Reflected in Actual Pairings?. PLOS ONE 8(1): e54186. https://doi.org/10.1371/journal.pone.0054186

