---
title: "Couples Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`couples.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/couples.csv)

<i class="fas fa-database"></i> [`husbandswives.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/husbandswives.csv)

### Description

These datasets contains samples of heterosexual married couples. The second dataset is taken from a 1980 study of the heights and weights of the adult population in Great Britain. They represent a random sample of married couples. 

### Variables---Couples Dataset

* Names: names of the husband and wife
* wAge: wife's age in years
* hAge: husband's age in years
* wHeight: wife's height in millimeters
* hHeight: husband's height in millimeters

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/couples.csv")
glimpse(DATA)
head(DATA)
```

### Variables---Husbands and Wives Dataset

* Age_Husband: husband's age in years when the data were collected
* Ht_Husband: husband's height in millimeters
* Age_Wife: wife's age in years when the data were collected
* Ht_Wife: wife's height in millimeters
* Age_Husb_at_Marriage: husband's age in years when the couple married
* Years_Married: how many years the couple has been married
* Age_Wife_At_Marriage: wife's age in years when the couple married
* Duration: whether or not the duration of the marriage is > 20

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/husbandswives.csv")
glimpse(DATA)
head(DATA)
```

### References

Source 1: https://dasl.datadescription.com/datafile/couples/ 

Source 2: Marsh, C. (1988) *Exploring Data*. Cambridge, UK: Polity Press, 315.

Chalabi, M. (2014, December 4). How Common Is It For A Man To Be Shorter Than His Partner? [Blog post]. Retrieved from https://fivethirtyeight.com/features/how-common-is-it-for-a-man-to-be-shorter-than-his-partner/

Chalabi, M. (2015, January 22). What’s The Average Age Difference In A Couple? [Blog post]. Retrieved from https://fivethirtyeight.com/features/whats-the-average-age-difference-in-a-couple/

Stulp G, Buunk AP, Pollet TV, Nettle D, Verhulst S (2013) Are Human Mating Preferences with Respect to Height Reflected in Actual Pairings?. PLOS ONE 8(1): e54186. https://doi.org/10.1371/journal.pone.0054186

<hr>
