---
title: "Diamond Quality Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      echo = FALSE,
                      comment = NA)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`diamondquality.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/diamondquality.csv)

### Description

Dataset of characteristics for round diamonds.

### Variables

* Carat.Size: size of the diamond in carats
* Color: color rating of the diamond
* Clarity: clarity rating of the diamond
* Depth: depth %, found by dividing the overall depth by the overall width
* Table: flat surface %, found by dividing the table facet width by overall width
* Cut: cut grade of the diamond
* Report: source of the ratings
* Price: diamond price in dollars

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/diamondquality.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: https://dasl.datadescription.com/datafile/diamond-quality/

<hr>

