---
title: "Diet Crackers Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<hr>

<i class="fas fa-database"></i> [dietcrackers.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/dietcrackers.csv)


### Description

Overweight women volunteered for a study to determine whether eating specially prepared crackers before a meal could help them lose weight. The participants were randomly assigned to eat crackers with different types of fiber (bran fiber, gum fiber, both bran and gum fiber, and a control cracker). Some of the women developed uncomfortable bloating and upset stomachs during the study. Researchers suspected that some of the crackers might be at fault. The study was paid for by the manufacturers of the gum fiber, who hoped this would be a new diet tool.


### Variables

* Bloat: severity of bloating
* Cracker: type of cracker

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/dietcrackers.csv")
glimpse(DATA)
head(DATA)
```


### References

Source: https://dasl.datadescription.com/datafile/diet/

