---
title: "Fast Food 2017 Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(comment = "", message = FALSE, warning = FALSE, echo = FALSE)
library(readr)
library(dplyr)
```

<hr>

<i class="fas fa-database"></i> [fastfood2017.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/fastfood2017.csv)

<i class="fas fa-database"></i> [cookoutburgers.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cookoutburgers.csv)


### Description

Data were collected in January 2017 from online nutritional information provided by fast food restaurant chains. Food items from each restaurant include various burgers, a breaded chicken sandwich, a grilled chicken sandwich, chicken nuggets, french fries, and a chocolate milkshake, when possible. The "various burgers" selected were the smallest hamburger, the smallest cheeseburger, and some of the restaurant's most well known larger burgers (e.g., Big Mac, Whopper). The Cookout data was sourced from https://www.fastfoodmenuprices.com/cookout-nutrition/.


### Variables

* restaurant: name of the fast food restaurant
* item: name of the food item
* type: type of food item (e.g., burger, chicken nuggets)
* servingsize: total serving size (g)
* calories: total calories
* totalfat: total fat (g)
* saturatedfat: total saturated fat (g)
* transfat: total trans fat (g)
* sodium: total sodium (mg)
* carbs: total carbs (g)
* sugars: total sodium (g)
* protein: total protein (g)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/fastfood2017.csv")
glimpse(DATA)
head(DATA)
```


### Variables

* burger: name of the burger
* calories: total calories
* fat: total fat (g)
* carbs: total carbs (g)
* protein: total protein (g)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cookoutburgers.csv")
head(DATA)
```


### References

Source: [StatCrunch dataset "Nutritional Data for Fast Food 2017"](https://www.statcrunch.com/app/index.php?dataid=2323899)
