---
title: "Galton Height Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<hr>

<i class="fas fa-database"></i> [galtonheightdata.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/galtonheightdata.csv)


### Description

Francis Galton, a cousin of Charles Darwin, studied the relationship between parent heights and the heights of their offspring. From his original article on regression, cited below: "My data consisted of the heights of 930 adult children and of their respective parentages, 205 in number. In every case I transmuted the female statures to their corresponding male equivalents and used them in their transmuted form... The factor I used was 1.08, which is equivalent to adding a little less than one-twelfth to each female height. It differs a very little from the factors employed by other anthropologists..." 

The dataset here was [created under the direction of Dr. James A. Hanley](http://www.medicine.mcgill.ca/epidemiology/hanley/galton/) from Galton's original paper notebooks, though eight families were left out for illustrative purposes. The "female statures" are in their raw (untransmuted) form.


### Variables

* Family: family the child belongs to, labeled 1 to 204 and 136A
* Father: father's height in inches
* Mother: mother's height in inches
* Gender: child's gender, male (M) or female (F)
* Height: child height in inches
* Kids: number of children in the child's family

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/galtonheightdata.csv")
glimpse(DATA)
```


### References

[Random Services: Galton's Height Data](http://www.randomservices.org/random/data/Galton.html)

Galton, Francis. (1886). Regression toward mediocrity in hereditary stature. _The Journal of the Anthropological Institute of Great Britain and Ireland_, 15, pp. 246-263.

