---
title: "Lego Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`lego816.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/lego816.csv)

### Description

The data contains Lego sets that were available on the Lego website in August 2016.

### Variables

* `number`: set ID number
* `name`: set name
* `price`: set price in USD
* `pieces`: number of pieces
* `minifigs`: number of mini figures
* `minifigsspec`: number of special mini figures
* `agemin`: minimum age listed on the box
* `agemax`: maximum age listed on the box
* `theme`: the set's general theme (e.g., `City`, `Star Wars`)
* `type`: the set's type (e.g., `Kids`, `Pop Culture`)
* `rating`: average user rating on a scale of 1 to 5
* `exclusive`: exclusive sets can only be bought from Lego (0 = no, 1 = yes) 
* `rare`: whether or not the set is considered to be rare (0 = no, 1 = yes) 

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/lego816.csv")
glimpse(DATA)
head(DATA)
```

### References

[Brickset: LEGO set guide and database | 2016](https://brickset.com/sets/year-2016)

[Rebrickable: LEGO Catalog Database Downloads](https://rebrickable.com/downloads/)

<hr>
