---
title: "Gay Marriage and Marijuana Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<hr>

<i class="fas fa-database"></i> [mmFEB2015.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/mmFEB2015.csv)


### Description

These data come from a [2015 Vox article](https://www.vox.com/2014/11/7/7169501/same-sex-marriage-marijuana-legalization-midterm-election-2014) examined the relationship between gay marriage and legal marijuana use in US states. 


### Variables

* state: state name
* marriage: whether gay marriage was legal in Feb 2015
* mgmethod: method by which gay marriage became legal
* mgyear: year in which gay marriage was legalized
* marijuana: whether marijuana use was legal in Feb 2015
* mjtype: type of legal marijuana use (none if illegal)
* mjmethod: method by which use marijuana was legalized
* mjyear: yearn which  marijuana use was legalized
* region: census region of the state

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/mmFEB2015.csv")
glimpse(DATA)
```


### References

Lopez, G. (2015, February 12). States where you can get high at a same-sex wedding, in one chart. [Blog post]. Retrieved from https://www.vox.com/2014/11/7/7169501/same-sex-marriage-marijuana-legalization-midterm-election-2014

Bump, P. (2014, November 5). This Venn diagram shows where you can both smoke weed and get a same-sex marriage. [Blog post]. Retrieved from https://www.washingtonpost.com/news/the-fix/wp/2014/11/05/this-venn-diagram-shows-where-you-can-both-smoke-weed-and-get-a-same-sex-marriage



