---
title: "Nail Polish Experiment Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      echo = FALSE,
                      comment = NA)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`nailpolish.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/nailpolish.csv)

### Description

A student preparing for a triathlon suspected that the time she spent training in the pool was damaging her nail polish. She wished to investigate whether the color of the nail polish might make a difference. To investigate this, she mounted acrylic nails on sticks and polished them with two different color nail polishes. She soaked them together in a chlorine solution equivalent to a swimming pool’s chlorination and then tapped them 100 times on a computer keyboard to simulate daily stress. The response is the % of nail chipped off as measured by scanning images of the nails and using an image processing program.

### Variables

* Color: nail polish color
* PctChipped: % of nail chipped off during stress testing

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/nailpolish.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: https://dasl.datadescription.com/datafile/nail-polish/

<hr>

