---
title: "NFL Players 2016 Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`NFLplayers2016.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/NFLplayers2016.csv)

<i class="fas fa-database"></i> [`NFLpositions.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/NFLpositions.csv)

### Description

Data about all National Football League (NFL) players in 2016.

### Variables---NFL Players 2016 Dataset

* `Jersey`: player jersey number
* `Name`: player name
* `Position`: player position
* `Age`: player age
* `Height`: player height in inches
* `Weight`: player weight in pounds
* `Years`: number of years played prior to the 2016 season
* `College`: college the player attended
* `Team`: team played for in the 2016 season
* `PositionGrp`: groupings for player positions (`Position`)
* `Side`:  offense, defense, or special teams
* `Playtime`: grouping for number of years played (`Years`)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/NFLplayers2016.csv")
glimpse(DATA)
head(DATA)
```

### Variables---NFL Positions Dataset

* `Position`: position abbreviation
* `PositionExp`: full position name
    
```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/NFLpositions.csv")
glimpse(DATA)
head(DATA)
```

### References

[Wikipedia: American Football Positions](https://en.wikipedia.org/wiki/American_football_positions)

[Wikipedia: Glossary of American Football Terms](https://en.wikipedia.org/wiki/Glossary_of_American_football_terms)

<hr>
