---
title: "Oscar Winner Ages Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`oscarages.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/oscarages.csv)<br>

### Description

In January 2007, ***Entertainment Weekly*** magazine featured a cover story about three Academy Award nominees for Best Actress---Meryl Streep (age 57), Judy Densch (age 72), and Helen Mirren (age 61)---with a cover tagline that proclaimed "The Silver Foxes Rule!" This theme continued inside, with the article focusing in large part on how old these three women were, relative to previous winners, and the perceived Hollywood bias in favor of younger actresses. This discussion persists in one form or another to this day. In March 2023, the website ***Gold Derby*** discussed the ages of the actor/actress nominees for the upcoming 2023 awards and noted, "Even though the industry and the Oscars have historically favored the young, especially when it comes to women, things have been trending in the opposite direction the past few years." *What does the data say?*

### Variables

ceremony	decade	category	name	age	title

* `ceremony`: year the ceremony was held
* `decade`: decade, e.g. 1980s and 2020s
* `category`: Oscar category (Best Actor, Best Actress, Best Supporting Actor, Best Supporting Actress)
* `name ` : winner's name
* `age` : winner's age at the time of their win (at the ceremony)
* `title` : title of the movie(s) for which the winner was nominated

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/oscarages.csv")
glimpse(DATA)
head(DATA)
tail(DATA)
```

### References

[Academy Awards Databases](https://www.oscars.org/oscars/awards-databases)

[Wikipedia: Academy Award for Best Actor](https://en.wikipedia.org/wiki/Academy_Award_for_Best_Actor)

[Wikipedia: Academy Award for Best Supporting Actor](https://en.wikipedia.org/wiki/Academy_Award_for_Best_Supporting_Actor)

[Wikipedia: Academy Award for Best Actress](https://en.wikipedia.org/wiki/Academy_Award_for_Best_Actress)

[Wikipedia: Academy Award for Best Supporting Actress](https://en.wikipedia.org/wiki/Academy_Award_for_Best_Supporting_Actress)

[Collins, Clark. (January 19, 2007). "Silver Streak," ***Entertainment Weekly*** # 916.](https://www.simplystreep.com/articles/200701entertainmentweekly/)

[Eng, Joyce. (March 7, 2923). "The Oscars could produce one of the oldest quartets of acting winners ever," ***Gold Derby (website)***. ](https://www.goldderby.com/article/2023/oscar-acting-winners-age/)
