---
title: "Pearson Height Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include=FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
```

<hr>

<i class="fas fa-database"></i> [pearsonheightdata.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/pearsonheightdata.csv)


### Description

Karl Pearson studied the relationship between the heights of men and their adult sons, similar to research done by his colleague [Francis Galton](galtonheightdata.html). Pearson’s original data was measured and rounded to the nearest inch. The authors of an introductory statistics tectbook added a small amount of random uniform noise "to render it continuous"---but not large enough to fundamentally change its meaning. 


### Variables

* father: father's height in inches
* son: son's height in inches

```{r, echo=FALSE, message=FALSE}
library(dplyr)
DATA <- read.csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/pearsonheightdata.csv")
glimpse(DATA)
```


### References

[Random Services: Pearson's Height Data](http://www.randomservices.org/random/data/Pearson.html)

[Pearson: Heights of Fathers and Sons](http://myweb.uiowa.edu/pbreheny/data/pearson.html)

Pearson, Karl and Lee, Alice. (1903). On the laws of inheritance in man. _Biometrika_, 2, pp. 357-462.

Freedman, David, Pisani, Robert, and Purves Roger. (2007). _Statistics (4th ed.)_. W. W. Norton & Company.

