---
title: "Popular Kids Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(comment = "", message = FALSE, warning = FALSE, echo = FALSE)
library(readr)
library(dplyr)
```

<hr>

<i class="fas fa-database"></i> [popular.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/popular.csv)


### Description

In 1992, researchers Melissa A. Chase and Gail M. Dummer of Michigan State University collected data from a sample of 4th, 5th, and 6th grade students who were enrolled in schools in Ingham and Clinton counties in order to study the role certain factors play in determining social status. They selected a stratified random sample from urban, suburban, and rural school districts, with the goal of having about 1/3 of the students come from each district type. The dataset contains some data from this study.

All of the selected students were asked to choose from three options what they would most like to do at school.

* make good grades
* be good at sports
* be popular

Regardless of how they answered the first question, all students were also asked to rank four factors according to what they thought would be most likely to make them well-liked (i.e., would make them popular) among their classmates. For example, a student might say looks are most important (1), followed by money (2), grades (3), and sports (4).

* getting good grades
* being good at sports
* being good-looking
* having a lot of money


### Variables

* gender: boy or girl
* grade: 4, 5, 6
* age: age in years
* district_type: the type of school district (rural, suburban, urban)
* top_goal: student's choice of what they would most like to do at school (grades, sports, popularity)
* grades_rank: rank of "making good grades" for popularity (1 = most important, 4 = least important)
* sports_rank: rank of "being good at sports" for popularity (1 = most important, 4 = least important)
* looks_rank: rank of "being handsome or pretty" for popularity (1 = most important, 4 = least important)
* money_rank: rank of "having lots of money" for popularity (1 = most important, 4 = least important)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/popular.csv")
glimpse(DATA)
```


### References

Chase, Melissa A. and Dummer, Gail M. (1992). The Role of Sports as a Social Determinant for Children. _Research Quarterly for Exercise and Sport_, 63(4), pp. 418-424. [[abstract]](https://www.ncbi.nlm.nih.gov/pubmed/1439167)

Chase, Melissa A. and Machida, Moe. (2011). The Role of Sport as a Social Status Determinant for Children: Thirty Years Later. _Research Quarterly for Exercise and Sport_, 82(4), pp. 731-739. [[abstract]](https://www.ncbi.nlm.nih.gov/pubmed/22276415) 

Lunscombe, Belinda (2011, February 8). Why Kids Bully: Because They’re Popular [blog post]. Retrieved from http://healthland.time.com/2011/02/08/do-popular-kids-bully-more/print/.
