---
title: "US Regions Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: 'Updated: `r format(Sys.time(), "%A, %B %d, %Y @ %X")`'
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`usregions.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/annualinflation.csv)

### Description

Includes some of the regional categorizations of the United States.

### Variables

* `state`: state name
* `census_region`: U.S. Census Bureau region
* `census_division`: U.S. Census Bureau sub-region 
* `economic_region`: Bureau of Economic Analysis region
* `ombfed_region`: Office of Management & Budget region 
* `court_circuit`: U.S. Courts of Appeals circuit
* `ars_region`: Agricultural Research Service region
* `park_region`: National Park Service region
* `padd_district1`: Petroleum Administration for Defense district
* `padd_district2`: Petroleum Administration for Defense districts with East Coast sub-districts

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/usregions.csv")
glimpse(DATA)
head(DATA)
```

### References

[Even the US government can't agree on how to divide up the states into regions](https://www.businessinsider.com/regions-of-united-states-2018-5#its-no-wonder-its-so-hard-to-say-once-and-for-all-which-states-are-in-which-regions-11)

[Wikipedia: List of regions in the United States](https://en.wikipedia.org/wiki/List_of_regions_of_the_United_States)

<hr>
