---
title: "US Skyscrapers Dataset"
author: "Instructor: Jill E. Thomley (thomleyje@appstate.edu)"
date: "Updated: `r format(Sys.time(), '%A, %B %d, %Y @ %X')`"
output: 
  html_document: 
    highlight: textmate
    theme: cosmo
---

```{r setup, include = FALSE}
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  comment = NA
)
library(readr)
library(dplyr)
```
<hr>

<i class="fas fa-database"></i> [`USskyscrapers.csv`](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/USskyscrapers.csv)

### Description

Data about structures in the United States that are $\ge$ 100 meters tall (as of ~2015).

### Variables

* Building: name of the structure
* City: city in which the structure is located
* Height: height in meters
* Floors: how many floors
* Completed: when construction was completed
* Material: primary construction material(s)
* Use: primary use(s)

```{r}
DATA <- read_csv("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/USskyscrapers.csv")
glimpse(DATA)
head(DATA)
```

### References

Source: StatCrunch public datasets 

<hr>
